VOCC outline

### 2020-04-25 ms/ms.Rmd

```{r worm-plots, fig.cap="Slopes of relationships between climate trends and percent change in biomasss (A; controlling for effect of the other climate variable) or biotic and climate velocities (B; without controlling for the effect of the other climate variable) for groundfish species. Open circles indicate patterns for immatures, while closed circles represent individuals large enough to have a 5\\% chance of being reproductively mature or belonging to species for which maturity data was not available. Black indicates the overall effect when the 95\\% CI of the estimated interaction with mean climate condition overlapped zero. Colours indicate slopes estimated for the low (0.025) and high (0.975) quantiles of mean climate conditions (only included when the confidence intervals on the slopes did not overlap). Coefficients are ordered by TODO within each panel.", out.width="5.2in"}
# include_graphics(here("ms", "figs", "worm-plot-trend.pdf"))
# TODO: decide if velocity slopes belong here
# TODO: should species be in same order on both trend and velocity panels?
include_graphics(here("ms", "figs", "worm-plot-both.pdf"))
```

>>>>

```{r worm-plots, fig.cap="Slopes of relationships between climate trends and percent change in biomasss controling for effect of the other climate variable for groundfish species. Open circles indicate patterns for immatures, while closed circles represent individuals large enough to have a 5\\% chance of being reproductively mature or belonging to species for which maturity data was not available. Black indicates the overall effect when the 95\\% CI of the estimated interaction with mean climate condition overlapped zero. Colours in legends indicate slopes estimated for the low (0.025) and high (0.975) quantiles of mean climate conditions. Coefficients are ordered by mean slope for each species within each panel.", out.width="5.2in"}
include_graphics(here("ms", "figs", "worm-plot-trend.pdf"))
# TODO: decide if velocity slopes belong here, removed them for now (04-23)
# TODO: should species be in same order on both trend and velocity panels?
# include_graphics(here("ms", "figs", "worm-plot-both.pdf"))
```
